---
title       : My ShinyApps on EPA National Ambient Air Quality Data
subtitle    : 
author      : Shafi
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
github:
  user:shafiab
  repo:slidifyDemo


--- .class #id 

## Description

- The shinyapps will present the EPA National Ambient Air Quality Data for the year 2013.
- The app shows the level of two pollutants for a given location
- The pollutants are:
  1. Ozone (ppm)
  2. PM2.5 (ug/m3)
-The app shows the levels of these two pollutants for a given area.

- The original code to get the pollutant data was taken from the lecture video on *yhat*.
- However, the original code require latitude, longitude and radius as input.

```{r, eval=F}
  pollutant(data.frame(lon=-76,lat=39,radius=40))
```

---

## R Code
- In my app, I added a wrapper function to get the latitute and longitude value using a lookup table.
```{r}
  ZIP<-read.csv("zipcode.csv")
  zipcode<-95054
  latitude<-ZIP$latitude[ZIP$zip==zipcode]
  longitude<-ZIP$longitude[ZIP$zip==zipcode]
  print(latitude)
  print(longitude)
```

---

## Input 

- The app takes two input

    1. Zipcode
    2. Radius  

- The user will input the zipcode in the text box.
- The default zipcode is set to *95054*
- User can enter any zip code within the US
- The calculated latitude and longitude values based on the entered zipcode are used as input to the pollutant function

- The user can select any radius from the slider
- The default radius is set to 40 miles

---

## Output
- Based on the user input, the app will show the city name, state
- The app will also show the pollutant levels for that city in a table
- The app also determine the city name and state using the lookup table and used in the app

- The app also contains a help document
- If user click the *Help Guide*, the app will take the user to a new page
- The new page contains a help guide for the users to use the app

